\section{Aspects of Anonymous Trading}

\subsection{Anonymous Entities}
\begin{frame}
    \frametitle{\insertsubsection}
    Different Levels of anonimity, different entities that can be anonymous.
    \vspace{1em}
    \begin{itemize}
        \itemsep\setlength{.8em}
        \item opportunities of anonymous trading
        \item anonymous vendors
        \item anonymous consumers
        \item anonymous platforms
    \end{itemize}
\end{frame}

\subsection{Opportunities of Anonymous Trading}
\begin{frame}
    \frametitle{\insertsubsection}
    \underline{Why are people doing it?}
    \vspace{2em}
    \begin{itemize}
        \itemsep\setlength{1em}
        \item positive (direct) effects
        \item negative sideeffects (no control possible by design, gov. cannot control, gov. cannot help / enforce law / käuferschutz)
        \item immoral goods (eg. weapons, drugs)
    \end{itemize}
\end{frame}

\subsection{Aspects of Vendor Morality}
\begin{frame}
    \frametitle{\insertsubsection}
    \underline{Offering anon trading: why should I (not) do it as a business / person?}
    \vspace{1em}
    \begin{itemize}
        \itemsep\setlength{1em}
        \item own profit?
        \item utilitarianism (everybodies profit?)
        \item shareholder theory
        \item stakeholder theory
    \end{itemize}
\end{frame}

\subsection{Daring to Consume}
\begin{frame}
    \frametitle{\insertsubsection}
    \underline{What can I expect the vendor to behave like and why?}\\
    \vspace{.8em}
    Consumer assumes to receive goods $\rightarrow$ assumes some ethical behavior of vendor.\\
    \vspace{1em}
    \underline{What can be assumed? Why are people assuming what?}
    \vspace{.8em}
    \begin{itemize}
        \itemsep\setlength{.8em}
        \item no legal liability $\rightarrow$ no justice ?% paid but got no goods? happens..
        \item silkroad/deep web $\rightarrow$ somehow works without justice enforced by 3rd party
        \item vendor reputation and trust in other peoples reports
        %\item assuming ethical attitudes -> the business I am dealing with has to somehow deal with this. assume it is interested in shareholders? stakeholders? stakeholders it feels like! why? 
    \end{itemize}
\end{frame}

\subsection{Enabling Anonymous Trading}
\begin{frame}
    \frametitle{\insertsubsection}
    %As a business and/or individual:\\
    \vspace{.4em}
    \underline{Is it ethical to build/offer software, that \emph{enables} anonymous trading?}\\
    %Is it morally OK to create / offer software, that helps / enables anonymous trading?
    \vspace{1em}
    \underline{What about offering / hosting platforms?}\\
    \vspace{1em}
    Different perspectives:\\
    \begin{itemize}
        \itemsep\setlength{.8em}
        \item Kantian Ethics
        \item Utilitarianism
        \item Shareholder
        \item Stakeholder
        \item My oppinion
    \end{itemize}
    Note: Maybe I will restrict some views here, due to brevity. Not decided yet.
\end{frame}