\section{Viewpoints on Vendor Morality}
\label{vendors}

Sellers on Silk Road typically sell a lot of different wares and not just one thing. For example, one seller specializes on drugs. Being a seller on Silk Road comes with the creation of a seller page, to offer multiple items on. Furthermore, being a seller comes with a fee to pay to the platform~\cite{silkroad2013}. Thus, vendors on Silk Road can be seen as a business. When running a business, one may consider different ethical viewpoints.

As an anonymous vendor, there is no need to actually send any goods, once a payment is received. As discussed, Silk Road enrolled a reputation system to overcome the trust dilemma. The remainder of this section assumes, that there is some driver for anonymous sellers to actually send out their goods. It covers the question, what ethical viewpoints or motives a sellers could have, to partake of anonymous online trading. Two well known ethical theories are reflected in the context of anonymous vendors behavior. First, Milton Friedman's shareholder theory \cite{shareholder} is applied to anonymous online market vendors. Second, the stakeholder theory by Edward Freeman \cite{stakeholder} is discussed in context.

\subsection{About the Law}

Both, shareholder and stakeholder theory come with the obligation to obey the law when running a business\cite{shareholder, stakeholder}. One can argue about anonymous online trading and the law. It strongly depends on what goods are sold and to what countries they are shipped. Exactly that is the point -- there are countries, where certain drugs or the possession of weapons are legal. As the seller is anonymous, we do not know what legal obligations apply. And as the trading happens fully anonymous, a seller cannot know which legal obligations frame his customers. In a fully anonymous context, nobody can possibly know what legal constraints apply to whom.

If it is unknown what legal obligations are forced upon some entity, does that entity have to obey all possible obligations (on the world) or none? I argue that we -- as external observers -- are in no position to judge. One cannot say whether it is legally wrong to buy or sell something, without knowing the law.

This applies for all the anonymized online communication, but what is with shipping goods? Again, it is notably that we do not know with certainty, if a seller breaks a law \emph{just by sending} goods to some country. So we cannot judge in a legal sense about the seller. Consumers are the only entities that have to specify a real world address for shipping. That is the only certainty we get when judging about the transaction in a legal sense. Considering the wares on Silk Road \cite{silkroad2013}, most probably consumers would break a law by receiving those goods in most countries of the world.

Keeping this in mind, we will discuss if anonymous sellers can act ethically.

\subsection{Shareholder Theory}

Mitlon Friedman proposed the shareholder theory in 1970. It basically states that the main responsibility of a business is to maximize its own profit. That is, as long the business obeys the law and ``ethical custom'' of the society\cite{shareholder}. 

Maximizing profit in the context of anonymous online trading, maybe on a deep web platform like Silk Road, is directly dependent on building up positive reputation. As pointed out in section~\ref{consumers}, positive reputation contributes to consumer trust, which is essential to keep an anonymous business running. That means, it is a sellers intrinsic motivation to make the consumers happy in order to gather positive reputation and keep up the business. Especially by shipping the goods.

Thus, from a shareholders perspective, an anonymous online seller acts ethically, when the business actions lead to positive reputation. The business keeps flourishing as long as the consumers are satisfied, which only can happen if the correct wares are shipped.

This causal chain is very easy to anticipate from a consumers perspective. When considering to buy something, consumers might ask themselves ``What can I expect the seller to behave like, and why?'' It seems very obvious for a consumer to anticipate, that a seller would at least want to maximize profit -- that a seller acts ethical at least up to their own interests. Along with the reputation system that surely leads to the conclusion that one will receive the wares. I think this is one of the main reasons why anonymous online trading works in general.

\subsection{Stakeholder Theory}

In 1984 Edward Freeman proposed the stakeholder theory\cite{stakeholder}. It includes not just shareholders, but any entity affected by business actions, such as employees or customers. Countries, or more precisely governments can be considered stakeholders on any kind of trade. The import of banned substances or weapons violates many governments interests. Generally, any import may concern a government, because tax fees may apply. Thus we can agree, that governments are stakeholders on anonymous online sellers. 

Customers are stakeholders as well. A customer decides at the time of the trade, to eventually break the law of the country she lives in. Nevertheless, it is a customers interest to receive the goods they paid for. That gives a potential conflict with governmental interests. If a seller obeys governmental interests and does not send any goods, that would conflict with the customers interest. On the other hand, if a seller serves up to customer interests, they eventually break some laws.

For anonymous online trading, most of the time sellers do not know in advance which country a consumer belongs to. Thus, a seller does not know in advance if serving this special customer could eventually break some laws. For example on Silk Road the shipping information becomes available after payment. A customer sends the money and some encrypted message where to ship to\cite{silkroad2013}. Once the money is received, the seller is left with the ethical conflict to send goods to a country where they could be banned. Anonymization during the trading process makes it impossible for a seller to exclude certain customers before the trade. The only way to avoid this potential conflict is to not sell at all to anonymous customers. Or to only sell goods that are definitely neither prohibited nor taxed by any country in the world, where potential customers could live.

It is impossible for a seller to act up to all stakeholders interests, when selling questionable goods to an anonymous audience. Consequently, anonymous online trading in the deep web can be considered unethical from a stakeholders perspective. There will always be conflicting interest between the different stakeholders. Thus, any deep web shop like Silk Road can be considered unethical, in the sense of the stakeholder theory.